### 2019-07-18 manuscript/discussion.tex
I edited (slightly) the Diploidization section. It's a bit shorter now, and very similar to Rosana's last version (in content).

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \emph{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication ( $71 \pm 19$ My, \citet{tomato2012})  likely pre-dating the origin of the family ($49 \pm 3$ My; \citealt{sarkinen_2013}). 
The age of the peak of paralog Ks distances is approximately $71 \pm 19$ My \citep{tomato2012}. 
%B: We cannot selectively delete the weak evidentiary basis for ku2000, blanc2004, and tomato2012. It's the only mention of their inference date and method, and it is a single sentence. %R- not entering into the weeds of Ks plots

% Part II: evidence against WGD in/near family
On the other hand, there is little evidence for the occurrence of diploidization after the origin of Solanaceae itself.
First, the Ks-inferred duplication \citep{tomato2012} pre-dates the origin of the family (49 My, HPD 46--53 My; \citealt{sarkinen_2013}). 
Studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution within species in the cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
Recovery of comparatively few rearrangements would require outstanding convergent loss of duplicated segments.
Furthermore, whole genome duplication in a eudicot lineage ancestral to Solanaceae would clash with the evidence that the homologous mechanism of SI, which has been present continually in many families \citep{igic_2006}, breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002, mcclure_2009}.
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in Solanaceae and other families if SI was previously broken down by polyploidization.
%
Regardless of whether genome polyploidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that more work is needed for a complete understanding of the joint evolution of ploidy and breeding systems.

>>>>

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to cultivated tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as genetic distances (Ks) between inferred paralogs within genomes of \emph{Solanum} (tomato and potato), each suggested that this lineage experienced a likely round of ancient genome duplication or triplication ( $71 \pm 19$ My, \citet{tomato2012})  likely pre-dating the origin of the family ($49 \pm 3$ My; \citealt{sarkinen_2013}).

% Part II: evidence against WGD in/near family
On the other hand, there is little evidence for the occurrence of diploidization after the origin of Solanaceae itself.
Studies comparing genetic map-based genome synteny within a number of species in this family find no evidence for diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution within species in the cytogenetically conserved `x=12' group, which includes tomato, potato, eggplant, pepper, and tobacco.
Recovery of comparatively few rearrangements would require outstanding convergent loss of duplicated segments.
Furthermore, whole genome duplication in a eudicot lineage ancestral to Solanaceae would clash with the evidence that the homologous mechanism of SI, which has been present continually in many families \citep{igic_2006}, breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002, mcclure_2009}.
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in Solanaceae and other families if SI was previously broken down by polyploidization.
%
Regardless of whether genome polyploidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that more work is needed for a complete understanding of the joint evolution of ploidy and breeding systems.
